Escape Analysis and Specialization in a Tracing JIT

### 2010-09-23 talk/pepm2011/paper.tex
move stuff around a bit

@@

This section is a bit
science-fictiony. The algorithm that PyPy currently uses is significantly more
complex and much harder than the one that is described here. The resulting
behaviour is very similar, however, so we will use the simpler version (and we
might switch to that at some point in the actual implementation).

@@

To understand some more what the optimization described in the last section
can achieve, look at the following figure:

\includegraphics{figures/obj-lifetime.pdf}

@@

>>>>

\section{Object Lifetimes in a Tracing JIT}
\label{sec:lifetimes}

% section Object Lifetimes in a Tracing JIT (end)

To understand the problems that this paper is trying to solve some more, we
first need to understand various cases of object lifetimes that can occur in a
tracing JIT compiler.

\begin{figure}
\includegraphics{figures/obj-lifetime.pdf}

\caption{Object Lifetimes in a Trace}
\label{fig:lifetimes}
\end{figure}

@@

@@

@@

\footnote{This section is a bit
science-fictiony. The algorithm that PyPy currently uses is significantly more
complex and much harder than the one that is described here. The resulting
behaviour is very similar, however, so we will use the simpler version (and we
might switch to that at some point in the actual implementation).}
